Cannibalism among the supermassive black holes

### 2018-09-12 paper.tex
Enlarged Kravtsov plot labels
Added van Dokkum references to Introduction, and pdfs of papers

How common are mergers of massive black holes?  For the galaxies themselves we know that minor mergers are frequent from the observed (VAN DOKKUM PAPERS??) evolution of the size and mass of these systems.  But assuming that all galaxy mergers lead to SMBH mergers overpredicts the observations of gravitational waves from the pulsar timing arrays (PTAs) (\citet{2008MNRAS.390..192S}, \citet{2009MNRAS.394.2255S}, \citet{2013MNRAS.433L...1S}, \citet{2014ApJ...789..156M}, \citet{2015ApJ...799..178K}, \citet{2018ApJ...856...42S}, \citet{2018arXiv180403143I}).  But we do not often see multiple SMBHs at the centers of massive ellipticals.  So, what does happen?  One paper (\citet{2018MNRAS.473.3410R}) has indicated that dynamical interactions among multiple black holes, which eject a non-negligible fraction of the mass, may solve this problem.  The present paper also addresses this purported dynamical solution, focusing attention on the large fraction of lower mass black holes that remain to be detected as they orbit in massive galaxies.  What we argue in this paper is that as a result of the N-body interactions among the infalling black holes some are ejected, some remain in extended orbits and some (the few most massive ones) do in fact merge, but these do not exceed the PTA limits, and the orbiting ones should be detectable via their ability to accrete gas and emit radiation.

@@

\subsubsection{Galactic Stellar Mass Adjustment}
Lackner12 noted that the efficiency of star formation in their simulations, defined as $f_*=M_*/M_{DM}(\Omega_{DM}/\Omega_b)$, was approximately 0.6.  Compared with the expected range of $0.10 \lessapprox f_* \lessapprox 0.15$ that they referenced from \citet{2012ApJ...746...95L}, their stellar masses were a factor of roughly 4 times greater.  We used observational data from \citet{2018AstL...44....8K}, in particular Figure 11, to rescale the stellar masses to the observed range (see Figure \ref{fig:stellar1}).
\begin{figure}[h!]
\begin{center}
\includegraphics[width=0.45\textwidth]{plots/stellar_to_halo_ratio.png}
\caption{Approximation of Figure 11 from \citet{2018AstL...44....8K}.  X's shown is example of our rescaled stellar masses}
\label{fig:stellar1}
\end{center}
\end{figure}

>>>>

How common are mergers of massive black holes?  For the galaxies themselves we know that minor mergers are frequent from the observed (\citet{2010ApJ...718L..73V}, \citet{2008ApJ...677L...5V}) evolution of the size and mass of these systems.  But assuming that all galaxy mergers lead to SMBH mergers overpredicts the observations of gravitational waves from the pulsar timing arrays (PTAs) (\citet{2008MNRAS.390..192S}, \citet{2009MNRAS.394.2255S}, \citet{2013MNRAS.433L...1S}, \citet{2014ApJ...789..156M}, \citet{2015ApJ...799..178K}, \citet{2018ApJ...856...42S}, \citet{2018arXiv180403143I}).  But we do not often see multiple SMBHs at the centers of massive ellipticals.  So, what does happen?  One paper (\citet{2018MNRAS.473.3410R}) has indicated that dynamical interactions among multiple black holes, which eject a non-negligible fraction of the mass, may solve this problem.  The present paper also addresses this purported dynamical solution, focusing attention on the large fraction of lower mass black holes that remain to be detected as they orbit in massive galaxies.  What we argue in this paper is that as a result of the N-body interactions among the infalling black holes some are ejected, some remain in extended orbits and some (the few most massive ones) do in fact merge, but these do not exceed the PTA limits, and the orbiting ones should be detectable via their ability to accrete gas and emit radiation.

@@

\subsubsection{Galactic Stellar Mass Adjustment}
Lackner12 noted that the efficiency of star formation in their simulations, defined as $f_*=M_*/M_{DM}(\Omega_{DM}/\Omega_b)$, was approximately 0.6.  Compared with the expected range of $0.10 \lessapprox f_* \lessapprox 0.15$ that they referenced from \citet{2012ApJ...746...95L}, their stellar masses were a factor of roughly 4 times greater.  We used observational data from \citet{2018AstL...44....8K}, in particular Figure 11, to rescale the stellar masses to the observed range (see Figure \ref{fig:stellar1}).
\begin{figure}[h!]
\begin{center}
\includegraphics[width=1.0\columnwidth]{plots/stellar_to_halo_ratio.png}
\caption{Approximation of Figure 11 from \citet{2018AstL...44....8K}.  X's shown is example of our rescaled stellar masses}
\label{fig:stellar1}
\end{center}
\end{figure}
